---
title: "Data Analysis Final Report"
author: "Eva Lüdke (820679) & Franziska Schwab (816512) "
date: "2023-03-31"
output:
  html_document:
    theme: cosmo
    toc: yes
    toc_float: true
  html_notebook: 
    theme: journal
    toc: true
    toc_float: true
  pdf_document:
    keep_tex: yes
    latex_engine: xelatex
fontsize: 12 pt
---

### Summary (5 points)

-   a short five-sentence abstract of your project

### Objectives (10 points)

-   What do you wish to analyse and why?

### Data description and general referencing (5 points)

This dataset describes the climate and energy indicators for Europe from 1979 to present derived from reanalysis and is sourced from the Copernicus climate change service (C3S) (DOI: 10.24381/cds.4bd77450): The parameters include climate variables and indicators from the energy sector which are:

-   Electricity demand (EDM [MWh])

-   Solar photovoltaic power generation (SPV [MW/MW])

-   Surface downwelling shortwave radiation (GHI [Wm-2])

    -   ("Downwelling shortwave radiation quantifies the direct energy from the sun as the sum of all wavelengths [...] Schmid, M., & Read, J.. (2022). Heat Budget of Lakes (pp. 467--473). <https://doi.org/10.1016/b978-0-12-819166-8.00011-6> )

-   Hydro power generation from reservoirs (HRE [W])

-   Hydro power generation from run-of-river (HRO [W])

-   2m Air temperature (TA [K])

-   Pressure at sea level (MSL [Pa])

-   Total precipitation (TP [K])

-   Wind power generation onshore (WON [MW/MW])

-   Wind speed at 100m (WS-10m [ms-1])

-   Wind speed at 10m (WS-100m [ms-1])

The dataset was subdivided into each parameter. Those had to be combined beforehand. Here, we chose a subset of the Europe Data, focusing only on the countries Germany and it's neighbouring countries Switzerland, and Denmark.

We wanted to analyze whether there is a visible difference between windspeed and onshore windpower generation between these countries. Therefore if the differences are sufficient that each country is classified into one cluster. Using the *K-means clustering* algorithm, the clusters are computed and data points assigned to each cluster.

```{r echo=FALSE,message=FALSE, warning=FALSE}
library(tidyverse)
library(tidymodels)
library(ggplot2)
library(dplyr)
library(tibble)
library(foreach)
library(GGally)

```

```{r echo=FALSE,message=FALSE, warning=FALSE}
knitr::opts_chunk$set(root.dir = "C:/Users/User/OneDrive/Dokumente/ClEWS-Data-Analysis")
```

```{r echo=FALSE,message=FALSE, warning=FALSE}
setwd("C:/Users/User/OneDrive/Dokumente/ClEWS-Data-Analysis")
```

### Preprocessing Data

```{r}
#Load each parameter 
#electricity demand in MWh (EDM [MWh])
electricity_demand_his <- read.csv("dataen/electricitydemand.csv")

#global horizontal irradiance in W m-2
irradiance_his <- read.csv("dataen/globalhoritontalirradiance.csv")

#hydropower reservoir (HRE) in W
hydropower_reservoir_his <- read.csv("dataen/hydropowerreservoir.csv")

#hydropower run-of-river (HRO) in W
hydropower_ro_his <- read.csv("dataen/hydropowerror.csv")

#mean sea level pressure in Pa
sealevelpressure_his <- read.csv("dataen/sealevelpressure.csv")

#solar pv power in MW/MW
solarpvpwr <- read.csv("dataen/solarpvpwr.csv")

#air temperature in K
air_temperature_his <- read.csv("dataen/airtemperature.csv")

#total precipitation in m
total_pr_his <- read.csv("dataen/totalpr.csv")

#wind power onshore in MW/MW
windpoweronshore_his <- read.csv("dataen/windpoweronshore.csv")

#wind speed in 10 m in m s-1
wind_speed_10_his <- read.csv("dataen/windspeed10.csv")

#wind speed in 100 m in ms-1
wind_speed_100_his <- read.csv("dataen/windspeed100.csv") 

```

```{r}
#insert missing columns for electricity_demand
electricity_demand <- electricity_demand_his

electricity_demand <- electricity_demand %>% add_column(AL=0, .after = "Date") %>% add_column(IS=0, .after="IE") %>% add_column(LI=0, .after = "IT") %>% add_column(MT=0, .after="MK") %>% add_column(TR=0, .after="SK")

```

```{r}

#add all variables into one dataframe

#countries <- c("AL","AT","BA","BE","BG","CH","CY","CZ","DE","DK","EE","EL","ES","FI","FR","HR","HU","IE","IS","IT","LI","LT","LU","LV","ME","MK","MT","NL","NO","PL","PT","RO","RS","SE","SI","SK","TR","UK")

#numbers <- c(2:39)

#for (i in seq_along(numbers)) {
  
#  print(paste(numbers[i],countries[i]))
#}

#select one Country from each dataframe
#`EDM [MWh]` <- electricity_demand %>% dplyr::select(1,39) 
#colnames(`EDM [MWh]`)[2] <- "EDM [MWh]"

#`GHI [Wm-2]` <- irradiance_his %>% dplyr::select(1,39)
#colnames(`GHI [Wm-2]`)[2] <- "GHI [Wm-2]"

#`HRE [W]` <- hydropower_reservoir_his %>% dplyr::select(1,39)
#colnames(`HRE [W]`)[2] <- "HRE [W]"

#`HRO [W]` <- hydropower_ro_his %>% dplyr::select(1,39)
#colnames(`HRO [W]`)[2] <- "HRO [W]"

#`MSL [Pa]` <- sealevelpressure_his %>% dplyr::select(1,39)
#colnames(`MSL [Pa]`)[2] <- "MSL [Pa]"

#`SPV [MW/MW]` <- solarpvpwr %>% dplyr::select(1,39)
#colnames(`SPV [MW/MW]`)[2] <- "SPV [MW/MW]"

#`TA [K]` <- air_temperature_his %>% dplyr::select(1,39)
#colnames(`TA [K]`)[2] <- "TA [K]"

#`TP [m]` <- total_pr_his%>% dplyr::select(1,39)
#colnames(`TP [m]`)[2] <- "TP [m]"

#`WON [MW/MW]` <- windpoweronshore_his %>% dplyr::select(1,39)
#colnames(`WON [MW/MW]`)[2] <- "WON [MW/MW]"

#`WS-10m [ms-1]` <- wind_speed_10_his %>% dplyr::select(1,39)
#colnames(`WS-10m [ms-1]`)[2] <- "WS-10m [ms-1]"

#`WS-100m [ms-1]` <- wind_speed_100_his %>% dplyr::select(1,39)
#colnames(`WS-100m [ms-1]`)[2] <- "WS-100m [ms-1]"

#merge dataframes together by Date

#UK <- Reduce(function(x,y) merge(x,y, all=TRUE), list(`EDM [MWh]`,`GHI [Wm-2]`,`HRE [W]`,`HRO [W]`,`MSL [Pa]`,`SPV [MW/MW]`,`TA [K]`,`TP [m]`,`WON [MW/MW]` ,`WS-10m [ms-1]`,`WS-100m [ms-1]`))

#add class "Country"
#UK$Country <- "UK"


#bind dataframes together 

newenergydata <- bind_rows(AL,AT,BA,BE,BG,CH,CY,CZ,DE,DK,EE,EL,ES,FI,FR,HR,HU,IE,IS,IT,LI,LT,LU,LV,ME,MK,MT,NL,NO,PL,PT,RO,RS,SE,SI,SK,TR,UK)
```

```{r}
newenergydata <-read.csv("newenergydata.csv",check.names=FALSE)
```

```{r}
#plot energydemand
ggplot(newenergydata) +
  geom_point(aes(y = `EDM [MWh]`, 
                 x = Date,
                 col = Country), alpha = 0.5)+
  labs(x = "Date [a]", y = "Energy Demand [MWh]") + 
  theme_bw()+
  theme(axis.text.x = element_text(angle=90, vjust=.5, hjust=1)) 

```

```{r}
#plot solar power
ggplot(newenergydata) +
  geom_point(aes(y = `SPV [MW/MW]`, 
                 x = Date,
                 col = Country), alpha = 0.5)+
  labs(x = "Date [a]", y = "Solar Power [MW/MW]") + 
  theme_bw()+
  theme(axis.text.x = element_text(angle=90, vjust=.5, hjust=1)) 

```

```{r}
#plot temperature
ggplot(newenergydata) +
  geom_point(aes(y =`TA [K]`, 
                 x = Date,
                 col = Country), alpha = 0.5)+
  labs(x = "Date [a]", y = "Temperature [K]") + 
  theme_bw()+
  theme(axis.text.x = element_text(angle=90, vjust=.5, hjust=1)) 
```

```{r}
#plot irradiance
ggplot(newenergydata) +
  geom_point(aes(y = `GHI [Wm-2]`, 
                 x = Date,
                 col = Country), alpha = 0.5)+
  labs(x = "Date [a]", y = "GHI [Wm-2]") + 
  theme_bw()+
  theme(axis.text.x = element_text(angle=90, vjust=.5, hjust=1)) 
```

```{r}
#plot hydropower reservoir
ggplot(newenergydata) +
  geom_point(aes(y = `HRE [W]`, 
                 x = Date,
                 col = Country), alpha = 0.5)+
  labs(x = "Date [a]", y = "HRE [W]") + 
  theme_bw()+
  theme(axis.text.x = element_text(angle=90, vjust=.5, hjust=1))
```

```{r}
#plot hydropower runoff
ggplot(newenergydata) +
  geom_point(aes(y = `HRO [W]`, 
                 x = Date,
                 col = Country), alpha = 0.5)+
  labs(x = "Date [a]", y = "HRO [W]") + 
  theme_bw()+
  theme(axis.text.x = element_text(angle=90, vjust=.5, hjust=1))
```

```{r}
#plot sea level pressure
ggplot(newenergydata) +
  geom_point(aes(y = `MSL [Pa]`, 
                 x = Date,
                 col = Country), alpha = 0.5)+
  labs(x = "Date [a]", y = "MSL [Pa]") + 
  theme_bw()+
  theme(axis.text.x = element_text(angle=90, vjust=.5, hjust=1))
```

```{r}
#plot total precipitation 
ggplot(newenergydata) +
  geom_point(aes(y = `TP [m]`, 
                 x = Date,
                 col = Country), alpha = 0.5)+
  labs(x = "Date [a]", y = "TP [m]") + 
  theme_bw()+
  theme(axis.text.x = element_text(angle=90, vjust=.5, hjust=1))
```

```{r}
#plot wind power onshore
ggplot(newenergydata) +
  geom_point(aes(y = `WON [MW/MW]`, 
                 x = Date,
                 col = Country), alpha = 0.5)+
  labs(x = "Date [a]", y = "WON [MW/MW]") + 
  theme_bw()+
  theme(axis.text.x = element_text(angle=90, vjust=.5, hjust=1))
```

```{r}
#plot wind speed 10m
ggplot(newenergydata) +
  geom_point(aes(y = `WS-10m [ms-1]`, 
                 x = Date,
                 col = Country), alpha = 0.5)+
  labs(x = "Date [a]", y = "WS-10m [ms-1]") + 
  theme_bw()+
  theme(axis.text.x = element_text(angle=90, vjust=.5, hjust=1))
```

```{r}
#plot wind speed 100m
ggplot(newenergydata) +
  geom_point(aes(y = `WS-100m [ms-1]`, 
                 x = Date,
                 col = Country), alpha = 0.5)+
  labs(x = "Date [a]", y = "WS-100m [ms-1]") + 
  theme_bw()+
  theme(axis.text.x = element_text(angle=90, vjust=.5, hjust=1))
```

```{r}

Germany <- subset(newenergydata, Country == "DE") 
Germany$Date <- NULL

ggpairs(Germany,diag = list(continuous="barDiag"))+
  theme_bw()
```

```{r}

```

### Methods 1: Applications of the linear model (20 points)

### Methods 2: Applications of tree-based models (20 points)

### Methods 3: Application of statistical testing (10 points)

### Methods 4: Application of XXX (15 points)

### K-means Clustering (15 points)

```{r}
#select the variables for classification
windenergy <- energydata %>%
  dplyr::select(Country,`WON [MW/MW]`, `WS-100m [ms-1]`)

#plot windenergy(windspeed)
ggplot(windenergy) +
  geom_point(aes(y = `WON [MW/MW]`, 
                 x = `WS-100m [ms-1]`,
                 col = Country), alpha = 0.5)+
  labs(x = "Windspeed in 100 m height [m/s]", y = "Wind power generation onshore [MW/MW]") + 
  theme_bw()

```

This figure shows the relation between windspeed at 100m and onshore wind power generation for Germany, Switzerland and Denmark. The countries are visibly seperated.

```{r}
#Run k-means cluster analysis 
(kmc <- windenergy %>% 
   dplyr::select(- Country) %>% 
   kmeans(centers = 3))

#choose 3 clusters
```

Cluster means comprises the calculated mean of each cluster for both parameters. The Clustering vector shows to what cluster each data point belongs.

```{r}
#gives out table that shows to which cluster each data point is assigned to
augment(kmc,windenergy)
```

The Countries Germany and Denmark both have two outliers which are sorted into an other countries class.

```{r}
#summary for each cluster
tidy(kmc)
```

```{r}
#plot cluster together with centroids
ggplot(augment(kmc, windenergy)) +
  geom_point(aes(x = `WS-100m [ms-1]`, 
                 y = `WON [MW/MW]`,
                 col = .cluster),
             alpha = 0.5) +
  geom_point(data = tidy(kmc),
             aes(x = `WS-100m [ms-1]`,
                 y = `WON [MW/MW]`), 
             pch = "+", size = 7)+
  labs(x = "Windspeed in 100 m height [m/s]", y = "Wind power generation onshore [MW/MW]")+ 
  theme_bw()

```

Some data points are now classified in a different class as before. Those shift the clusters estimated centroids.

With adding more clusters we wanted to see if the outliers are sorted in extra cluster. To see how many different cluster seems to be useful in this case.

```{r}
(clust_test <- tibble(k = 1:9) %>%
  mutate(
    models = map(k, ~kmeans(windenergy[ , -1], .x))
    )
 )

```

```{r}
clust_test$models[5]

```

```{r}
(clust_test <- tibble(k = 1:9) %>%
  mutate(
    models = map(k, ~kmeans(windenergy[ , -1], .x)),
    points = map(models, augment, windenergy))
 )

```

```{r}
clust_test_pl <- unnest(clust_test, points)
head(clust_test_pl)

```

```{r}
#plot
ggplot(clust_test_pl) +
  geom_point(aes(x = `WS-100m [ms-1]`, 
                 y = `WON [MW/MW]`,
                 col = .cluster),
             alpha = 0.3) +
    facet_wrap( ~ k) +
  labs(x = "Windspeed in 100 m height [m/s]", y = "Wind power generation onshore [MW/MW]")+ 
  theme_bw()


```

In this plot we see a gradual increase of cluster centers/classes from 1 to 9 cluster. With these plots we can see that the outliers are not exclusively classified as their own class but the larger Groups are more and more divided. With 3 or 5 different cluster it seems to fit the best.

Another country - France - can be selected with similar wind speed values to those of Germany.

```{r}
#select only France from each dataframe
`EDM [MWh]` <- electricity_demand_his %>% dplyr::select(1,15) 
colnames(`EDM [MWh]`)[2] <- "EDM [MWh]"

`GHI [Wm-2]` <- irradiance_his %>% dplyr::select(1,16)
colnames(`GHI [Wm-2]`)[2] <- "GHI [Wm-2]"

`HRE [W]` <- hydropower_reservoir_his %>% dplyr::select(1,16)
colnames(`HRE [W]`)[2] <- "HRE [W]"

`HRO [W]` <- hydropower_ro_his %>% dplyr::select(1,16)
colnames(`HRO [W]`)[2] <- "HRO [W]"

`MSL [Pa]` <- sealevelpressure_his %>% dplyr::select(1,16)
colnames(`MSL [Pa]`)[2] <- "MSL [Pa]"

`SPV [MW/MW]` <- solarpvpwr %>% dplyr::select(1,16)
colnames(`SPV [MW/MW]`)[2] <- "SPV [MW/MW]"

`TA [K]` <- air_temperature_his %>% dplyr::select(1,16)
colnames(`TA [K]`)[2] <- "TA [K]"

`TP [m]` <- total_pr_his%>% dplyr::select(1,16)
colnames(`TP [m]`)[2] <- "TP [m]"

`WON [MW/MW]` <- windpoweronshore_his %>% dplyr::select(1,16)
colnames(`WON [MW/MW]`)[2] <- "WON [MW/MW]"

`WS-10m [ms-1]` <- wind_speed_10_his %>% dplyr::select(1,16)
colnames(`WS-10m [ms-1]`)[2] <- "WS-10m [ms-1]"

`WS-100m [ms-1]` <- wind_speed_100_his %>% dplyr::select(1,16)
colnames(`WS-100m [ms-1]`)[2] <- "WS-100m [ms-1]"

#merge dataframes together by Date

France <- Reduce(function(x,y) merge(x,y, all=TRUE), list(`EDM [MWh]`,`GHI [Wm-2]`,`HRE [W]`,`HRO [W]`,`MSL [Pa]`,`SPV [MW/MW]`,`TA [K]`,`TP [m]`,`WON [MW/MW]` ,`WS-10m [ms-1]`,`WS-100m [ms-1]`))

#add class "Country"
France$Country <- "FR"

```

```{r}
newenergydata <- bind_rows(energydata,France)

#select the variables for classification
newwindenergy <- newenergydata %>%
  dplyr::select(Country,`WON [MW/MW]`, `WS-100m [ms-1]`)

#plot windenergy(windspeed)
ggplot(newwindenergy) +
  geom_point(aes(y = `WON [MW/MW]`, 
                 x = `WS-100m [ms-1]`,
                 col = Country), alpha = 0.5)+
    labs(x = "Windspeed in 100 m height [m/s]", y = "Wind power generation onshore [MW/MW]")+ 
    theme_bw()

```

The "group" France lies inbetween the other countries. Now the analysis can be run with 4 cluster centers.

```{r}
#Run k-means cluster analysis 
(kmc2 <- newwindenergy %>% 
   dplyr::select(- Country) %>% 
   kmeans(centers = 4)) #choose 4 clusters

```

```{r}
augment(kmc2,newwindenergy)

```

```{r}
#summary for each cluster
tidy(kmc2)
```

```{r}
#plot cluster together with centroids
ggplot(augment(kmc2, newwindenergy)) +
  geom_point(aes(x = `WS-100m [ms-1]`, 
                 y = `WON [MW/MW]`,
                 col = .cluster),
             alpha = 0.5) +
  geom_point(data = tidy(kmc2),
             aes(x = `WS-100m [ms-1]`,
                 y = `WON [MW/MW]`), 
             pch = "+", size = 7) +
    labs(x = "Windspeed in 100 m height [m/s]", y = "Wind power generation onshore [MW/MW]")+ 
    theme_bw()

```

Adding another country changes the cluster centroids and classifications.

### Discussion and Conclusions (15 points)

-   What did you learn from your data analysis?
-   How could this be improved?
-   etc.
