---
title: "R Notebook"
output: html_notebook
---

```{r}
setwd("C:/Users/User/OneDrive/Dokumente/ClEWS-Data-Analysis")
knitr::opts_chunk$set(root.dir ="C:/Users/User/OneDrive/Dokumente/ClEWS-Data-Analysis")

```

```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(tidymodels)
```



```{r}
#electricity demand in MWh (EDM [MWh]) 
electricity_demand_his <- read.csv("dataen/electricitydemand.csv")

#global horizontal irradiance in W m-2
irradiance_his <- read.csv("dataen/globalhoritontalirradiance.csv")


#hydropower reservoir (HRE) in W

hydropower_reservoir_his <- read.csv("dataen/hydropowerreservoir.csv")

#hydropower run-of-river (HRO) in W

hydropower_ro_his <- read.csv("dataen/hydropowerror.csv")

#mean sea level pressure in Pa
sealevelpressure_his <- read.csv("dataen/sealevelpressure.csv")


#solar pv power in MW/MW

solarpvpwr <- read.csv("dataen/solarpvpwr.csv")


#air temperature in K

air_temperature_his <- read.csv("dataen/airtemperature.csv")

#total precipitation in m

total_pr_his <- read.csv("dataen/totalpr.csv")

#wind power onshore in MW/MW
windpoweronshore_his <- read.csv("dataen/windpoweronshore.csv")

#wind speed in 10 m in m s-1
wind_speed_10_his <- read.csv("dataen/windspeed10.csv")


#wind speed in 100 m in ms-1
wind_speed_100_his <- read.csv("dataen/windspeed100.csv")



```


```{r}
# select Deutschland from Data frame
`EDM [MWh]` <- electricity_demand_his %>% select(1,9) 
colnames(`EDM [MWh]`)[2] <- "EDM [MWh]"

`GHI [Wm-2]` <- irradiance_his %>% select(1,10)
colnames(`GHI [Wm-2]`)[2] <- "GHI [Wm-2]"

`HRE [W]` <- hydropower_reservoir_his %>% select(1,10)
colnames(`HRE [W]`)[2] <- "HRE [W]"

`HRO [W]` <- hydropower_ro_his %>% select(1,10)
colnames(`HRO [W]`)[2] <- "HRO [W]"

`MSL [Pa]` <- sealevelpressure_his %>% select(1,10)
colnames(`MSL [Pa]`)[2] <- "MSL [Pa]"

`SPV [MW/MW]` <- solarpvpwr %>% select(1,10)
colnames(`SPV [MW/MW]`)[2] <- "SPV [MW/MW]"

`TA [K]` <- air_temperature_his %>% select(1,10)
colnames(`TA [K]`)[2] <- "TA [K]"

`TP [m]` <- total_pr_his%>% select(1,10)
colnames(`TP [m]`)[2] <- "TP [m]"

`WON [MW/MW]` <- windpoweronshore_his %>% select(1,10)
colnames(`WON [MW/MW]`)[2] <- "WON [MW/MW]"

`WS-10m [ms-1]` <- wind_speed_10_his %>% select(1,10)
colnames(`WS-10m [ms-1]`)[2] <- "WS-10m [ms-1]"

`WS-100m [ms-1]` <- wind_speed_100_his %>% select(1,10)
colnames(`WS-100m [ms-1]`)[2] <- "WS-100m [ms-1]"


Germany <- Reduce(function(x,y) merge(x,y, all=TRUE), list(`EDM [MWh]`,`GHI [Wm-2]`,`HRE [W]`,`HRO [W]`,`MSL [Pa]`,`SPV [MW/MW]`,`TA [K]`,`TP [m]`,`WON [MW/MW]` ,`WS-10m [ms-1]`,`WS-100m [ms-1]`))


Germany$Country <- "DE"


```

```{r}
# select DK
`EDM [MWh]` <- electricity_demand_his %>% select(1,10) 
colnames(`EDM [MWh]`)[2] <- "EDM [MWh]"

`GHI [Wm-2]` <- irradiance_his %>% select(1,11)
colnames(`GHI [Wm-2]`)[2] <- "GHI [Wm-2]"

`HRE [W]` <- hydropower_reservoir_his %>% select(1,11)
colnames(`HRE [W]`)[2] <- "HRE [W]"

`HRO [W]` <- hydropower_ro_his %>% select(1,11)
colnames(`HRO [W]`)[2] <- "HRO [W]"

`MSL [Pa]` <- sealevelpressure_his %>% select(1,11)
colnames(`MSL [Pa]`)[2] <- "MSL [Pa]"

`SPV [MW/MW]` <- solarpvpwr %>% select(1,11)
colnames(`SPV [MW/MW]`)[2] <- "SPV [MW/MW]"

`TA [K]` <- air_temperature_his %>% select(1,11)
colnames(`TA [K]`)[2] <- "TA [K]"

`TP [m]` <- total_pr_his%>% select(1,11)
colnames(`TP [m]`)[2] <- "TP [m]"

`WON [MW/MW]` <- windpoweronshore_his %>% select(1,11)
colnames(`WON [MW/MW]`)[2] <- "WON [MW/MW]"

`WS-10m [ms-1]` <- wind_speed_10_his %>% select(1,11)
colnames(`WS-10m [ms-1]`)[2] <- "WS-10m [ms-1]"

`WS-100m [ms-1]` <- wind_speed_100_his %>% select(1,11)
colnames(`WS-100m [ms-1]`)[2] <- "WS-100m [ms-1]"


Denmark <- Reduce(function(x,y) merge(x,y, all=TRUE), list(`EDM [MWh]`,`GHI [Wm-2]`,`HRE [W]`,`HRO [W]`,`MSL [Pa]`,`SPV [MW/MW]`,`TA [K]`,`TP [m]`,`WON [MW/MW]` ,`WS-10m [ms-1]`,`WS-100m [ms-1]`))


Denmark$Country <- "DK"


```
```{r}
#select only Switzerland from each dataframe
`EDM [MWh]` <- electricity_demand_his %>% select(1,6) 
colnames(`EDM [MWh]`)[2] <- "EDM [MWh]"

`GHI [Wm-2]` <- irradiance_his %>% select(1,7)
colnames(`GHI [Wm-2]`)[2] <- "GHI [Wm-2]"

`HRE [W]` <- hydropower_reservoir_his %>% select(1,7)
colnames(`HRE [W]`)[2] <- "HRE [W]"

`HRO [W]` <- hydropower_ro_his %>% select(1,7)
colnames(`HRO [W]`)[2] <- "HRO [W]"

`MSL [Pa]` <- sealevelpressure_his %>% select(1,7)
colnames(`MSL [Pa]`)[2] <- "MSL [Pa]"

`SPV [MW/MW]` <- solarpvpwr %>% select(1,7)
colnames(`SPV [MW/MW]`)[2] <- "SPV [MW/MW]"

`TA [K]` <- air_temperature_his %>% select(1,7)
colnames(`TA [K]`)[2] <- "TA [K]"

`TP [m]` <- total_pr_his%>% select(1,7)
colnames(`TP [m]`)[2] <- "TP [m]"

`WON [MW/MW]` <- windpoweronshore_his %>% select(1,7)
colnames(`WON [MW/MW]`)[2] <- "WON [MW/MW]"

`WS-10m [ms-1]` <- wind_speed_10_his %>% select(1,7)
colnames(`WS-10m [ms-1]`)[2] <- "WS-10m [ms-1]"

`WS-100m [ms-1]` <- wind_speed_100_his %>% select(1,7)
colnames(`WS-100m [ms-1]`)[2] <- "WS-100m [ms-1]"

#merge dataframes together by Date

Switzerland <- Reduce(function(x,y) merge(x,y, all=TRUE), list(`EDM [MWh]`,`GHI [Wm-2]`,`HRE [W]`,`HRO [W]`,`MSL [Pa]`,`SPV [MW/MW]`,`TA [K]`,`TP [m]`,`WON [MW/MW]` ,`WS-10m [ms-1]`,`WS-100m [ms-1]`))

#add class "Country"
Switzerland$Country <- "CH"


```


```{r}
ggplot(Germany) + 
  geom_point(aes(x = Date, 
                 y = `GHI [Wm-2]`)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

```{r}
energydata <- bind_rows(Germany, Switzerland, Denmark)

```

```{r}
windenergy <- energydata %>%
  select(Country,`WON [MW/MW]`, `WS-100m [ms-1]`)

ggplot(windenergy) +
  geom_point(aes(x = `WS-100m [ms-1]`, 
                 y = `WON [MW/MW]`,
                 col = Country), alpha = 0.5) +
  labs(x = "Windspeed in 100 m height [m/s]", y = "Wind power generation onshore [MW/MW]") + 
  theme_bw()
  

```
```{r}
# Run k-means cluster analyis
(kmc <- windenergy %>%
   select(- Country) %>% ### Was bedeutet das minus vor Country?
   kmeans(centers = 3))  # Sets the number of clusters 

```

```{r}
augment(kmc, windenergy)

```
The Countries Germany and Denmark both have two outliers which are sorted into an other countries class. 


```{r}
tidy(kmc)

```

```{r}
ggplot(augment(kmc, windenergy)) +
  geom_point(aes(x = `WS-100m [ms-1]`, 
                 y = `WON [MW/MW]`,
                 col = .cluster),
             alpha = 0.5) +
  geom_point(data = tidy(kmc),
             aes(x = `WS-100m [ms-1]`,
                 y = `WON [MW/MW]`), 
             pch = "+", size = 7)+
  labs(x = "Windspeed in 100 m height [m/s]", y = "Wind power generation onshore [MW/MW]")+ 
  theme_bw()

```
The Data points which are classified as a different class shift the clusters estimated centroids.
```{r}
(clust_test <- tibble(k = 1:9) %>%
  mutate(
    models = map(k, ~kmeans(windenergy[ , -1], .x))
    )
 )

```

```{r}
clust_test$models[5]

```

```{r}
(clust_test <- tibble(k = 1:9) %>%
  mutate(
    models = map(k, ~kmeans(windenergy[ , -1], .x)),
    points = map(models, augment, windenergy))
 )

```

```{r}
clust_test_pl <- unnest(clust_test, points)
head(clust_test_pl)

```
With adding more clusters we wanted to see if the outliers are sorted in extra cluster. To see how many different cluster seems to be useful in this case. 
```{r}
ggplot(clust_test_pl) +
  geom_point(aes(x = `WS-100m [ms-1]`, 
                 y = `WON [MW/MW]`,
                 col = .cluster),
             alpha = 0.3) +
    facet_wrap( ~ k) +
  labs(x = "Windspeed in 100 m height [m/s]", y = "Wind power generation onshore [MW/MW]")+ 
  theme_bw()


```
With these plots we can see that the outliers are not exclusively classified as their own class but the larger Groups are more and more divided. With 3 or 5 different cluster it seems to fit the best.


todo:

-Achsen beschriften X
-Plots verschönern X
-Interpretation für output
-Erklärung für warum Länderauswahl
-+1 extraland plot (4 cluster?)
